---
title: "Data sets"
date: "12 April 2016"
output: 
  github_document: 
    toc: yes
    toc_depth: 3
---

This is a collection of both "real" and example data useful for the illustration 
of different aspects related to data science (e.g. visualization, modeling or
statistical thinking in general).

## ggplot2movies

**Description**: Information and user ratings on 58'788 movies from <http://.IMDB.com>. 
The data set contains all movies until 2005 that had at least one vote.
There are 24 variables:  

1.  `title`: Title of the movie
2.  `year`: Year the movie was released
3.  `length`: Length in minutes
4.  `budget`: Total movie budget in US dollars
5.  `rating`: Average IMDB user rating
6.  `votes`: Number of IMDB users who rated the movie
7.  `r1-r10`: If multiplied by 10 the variables `r1` to `r10` give the percentiles 
of users who rated the movie with 1 star (worst possible rating)
8.  `mpaa`: Movie rating by the Motion Picture Association of America (MPAA), 
an association representing the six biggest Hollywood studios
9.  `Action-Short`: Seven dummies indicating the movie genre. Variable names are: 
Action, Animation, Comedy, Drama, Documentary, Romance, Short.

**Most useful for**: Cross-sectional analysis, visualization, modeling    
**Version info**: Version `0.0.1` of the `ggplot2movies` package as of December 2015.  
**How to get it**:    
  + In R: 
```{r eval=FALSE}
install.packages("ggplot2movies")
library(ggplot2movies)
data("movies")
```

## ggplot2::mpg

**Description**: The dataset contains a subset of the fuel economy data that the 
Environmental Protection Agency (EPA) makes available on <http://fueleconomy.gov>. 
It contains only models which had a new release every year between 1999 and 2008, 
resulting in 234 observation on 38 unique models of car. There are 11 variables:

1.  `manufacturer`: Name of the company that produced the car
2.  `model`: Name of the model
3.  `displ`: Engine displacement in liters
4.  `year`: Year the car was released
5.  `cyl`: Number of cylinders
6.  `trans`: Type of transmission.
7.  `drv`:  Drivetrain. Possible values: f=front wheel, r=rear wheel, 4=four wheel
8.  `cty`: Miles per gallon (mpg) for city driving
9.  `hwy`: Miles per gallon (mpg) for highway driving
10. `fl`: Fuel type: Possible values: c=CNG, d=diesel, e=ethanol E85, p=premium, r=regular
11. `class`: Class or type of car. Possible values: compact, subcompact, midsize, minivan, pickup, suv, 2seater

**Most useful for**: Visualization, simple modeling.  
**Version Info**: dataset as contained in ggplot2 version `2.0.0` (December 2015).   
**How to get it**:  
  + In R: 
```{r eval=FALSE}
install.packages("ggplot2")
library(ggplot2)
data("mpg")
```

## ggplot2::txhousing

**Description**: Information about the housing market in Texas provided by the [real estate center of the Texas A&M University (TAMU)](http://recenter.tamu.edu/). Data on all variables was collected on a monthly basis from January 2000 to July 2015 with 187 observations for each of the 46 Texan cities within the dataset, totaling the number of observations to 8602. There are 9 variables:

1.  `city`: Name of the city/ares according to the multiple listing service (MLS) classification
2.  `year`: Year observation was made
3.  `month`: Month observation was made
4.  `sales`: Total number of housing sales
5.  `volume`: Total volume of the sales
6.  `median`: Median sales price
7.  `listings`: Total active listings
8.  `inventory`: Number of month it would take to sell the current listings at the current pace of sales.
9.  `date`: Date observation was made as a combination of `year` and `month` where each month is a twelfth.

**Most useful for**: Time-series analysis, seasonal trends, visualization, modeling.  
**Version Info**: dataset as contained in ggplot2 version `2.0.0` (December 2015).   
**How to get it**:  
  + In R: 
```{r eval=FALSE}
install.packages("ggplot2")
library(ggplot2)
data("txhousing")
```

## nycflights13

**Description**: The main data set `flights` contains Information about all flights that departed from NYC (e.g. EWR, JFK and LGA) in 2013. This amounts to a total of 336,776 flights. To help understand what causes delays, it also includes a number of other useful datasets such as

  - `weather` : hourly meterological data for LGA, JFK and EWR.
  - `airlines`: airline names and carrier codes
  - `airports`: airport metadata such location and timezone
  - `planes`  : plane metadata such as speed, model etc.


**Most useful for**: Visualization, modeling, seasonal trends, time-series and cross-sectional regression.  
**Version Info**: version `0.0.1`  
**How to get it**:  
  + In R:
```{r eval=FALSE}
install.packages("nycflights13")
library(nycflights13)
data("flights"); data("planes"); data("airlines"); data("airports"); data("weather")
```
